The Effects of Varying Depth in Cosmic Shear Surveys

### 2019-06-21 paperdraft.tex
cleanup

   \author{S. Heydenreich\inst{1}%\fnmsep\thanks{sven@astro.uni-bonn.de}
          \and Peter Schneider\inst{1} 
          \and Hendrik Hildebrandt\inst{2,1}
          \and Catherine Heymans\inst{3} 
          \and Marika Asgari\inst{3}
          \todo{order of authors?, KiDS-Authors?}
          }
   \institute{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany 
\and 
Astronomisches Institut, Ruhr-Universit\"at Bochum, Universit\"atsstr. 150, 44801 Bochum, Germany \and
Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK  \\ \email{sven@astro.uni-bonn.de}
             }

@@

To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citep{2002ApJ...568...20C,2002A&A...389..729S}. To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics. Note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.

@@

@@

\section{Modelling the shear correlation functions}
\label{sec:xipm}
Convenient measures to infer cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \[
\xi_\pm(\theta) = \la \gamma_{\rm t}\gamma_{\rm t}\ra(\theta) \pm \la \gamma_\times\gamma_\times\ra(\theta) \, .
\]
Here, $\gamma_t$ and $\gamma_\times$ denote the tangential- and cross-component of the shear for a galaxy pair with respect to their relative orientation \citep[compare][]{2002A&A...396....1S}.
The shear correlation functions are the prime estimators to quantify a cosmic-shear signal since it is simple to include a weighting of the shear measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint, or masked regions. Given two comoving distance probability distributions of sources $p_i(\chi),p_j(\chi)$, one can compute the shear correlation functions from the underlying matter power spectrum $P_\delta(\ell,\chi)$ via \citep[compare][]{1992ApJ...388..272K} \begin{align}
\label{eq:xipm-pkappa}
\xi_\pm^{ij}(\theta) =& \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta)\, P^{ij}(\ell)\, , \\
\label{eq:pkappa-pdelta/lenseff}
P^{ij}(\ell) =& \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4}\int_0^{\chi_{\rm{H}}} {\rm d}\chi\, \frac{g^i(\chi)g^j(\chi)}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right)\, , \\
\label{eq:lenseff}
g^i(\chi) =& \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, p_i(\chi') \, \frac{f_K(\chi'-\chi)}{f_K(\chi')}\, .
\end{align}
Here, $J_{0,4}$ denote the 0-th and 4-th order Bessel Functions, $f_K(\chi)$ is the comoving angular diameter distance and $\chi_{\rm{H}}$ is chosen such that $p_i(\chi)=0$ holds for all $\chi>\chi_{\rm{H}}$.
\subsection{Using an analytic model}
\label{sec:xipm_analytic}
For a first simple analysis we will assume that a deeper redshift distribution just yields a stronger shear signal, in the sense that the shear field for a deeper redshift distribution gets multiplied by a weight $W>1$. While this is not true for a 3-dimensional lensing matter distribution, it should be a reasonable first approximation for small variations in mean source redshift. Additionally, we assume that a higher depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.

@@

\subsection{Using a semi-analytic Model}
\label{sec:xipm_semianalytic}
\todo{It feels like some kind of introductory sentence is missing here, right now I can not think of one, though...}
The analysis of data from the Kilo-Degree Survey showed that the redshift distribution of sources is highly correlated with the depth in the $r$-band. We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, i.e. if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first percentile, and so on. For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and, a source redshift distribution $p^i_m(z)$ following the DIR method of H17\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17. Due to this we account for different weighting of galaxies on the shear correlation functions as well as on the average redshift distribution.}. Using \eqref{eq:xipm-pkappa}, we can compute the model correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each pair of percentiles $m,n$ and redshift bins $i,j$.\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program \citep{10.1093/mnras/stx2082}. Among other quantities, it calculates the shear correlation functions for a given cosmology and source redshift distribution. For the power spectrum on nonlinear scales, we use the method of \citet{2012ApJ...761..152T}.} When measuring the shear correlation functions of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (compare H17). If, for a single pair of galaxies, one galaxy lies in the $m$-th percentile of redshift bin $i$ and the second one lies in the $n$-th percentile of redshift bin $j$, then their contribution to the observed correlation functions is, on average, $\xi_{\pm,mn}^{ij}(\theta)$. This means that if we know each of those single correlation functions, we can reconstruct the total correlation functions via a weighted average of the single functions. Formally, we define \[
\xi_\pm^{ij,\rm{obs}}(\theta) = \frac{\sum_{m,n} \mathcal{P}_{mn}^{ij}(\theta)\,\xi_{\pm,mn}^{ij}(\theta)}{\sum_{m,n} \mathcal{P}_{mn}^{ij}(\theta)}\, ,
\label{eq:def_xiobs}
\]
where $\mathcal{P}_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$.\todo{We \textit{could} completely scratch this derivation and just point to the Appendix; I personally feel that this approach is more intuitive than the more mathematical one of the appendix, but if the paper gets too long we definitely do not need two methods to derive the same equation.} In this analysis, we will assume an infinitely large survey footprint with an uncorrelated distribution of depth. We will later discuss the validity of these assumptions as well as possible mitigation strategies.

To calculate $\mathcal{P}_{mn}^{ij}(\theta)$ we imagine two arbitrary (infinitesimally small) surface elements $\d^2\b\theta_1,\d^2\b\theta_2$ of separation $\theta$ on the sky. For the case $m\neq n$ we know that a pair of galaxies contributing to $\mathcal{P}_{mn}^{ij}(\theta)$ has to lie in different pointings, else they would automatically be of the same percentile. The probability that the imagined surface elements are within different pointings is $[1-E(\theta)]$. Furthermore, the first element $\d^2\b\theta_1$ has to lie in percentile $m$, the probability of which is $1/10$. The pointing of the second element $\d^2\b\theta_2$ has to be of percentile $n$; the probability of that is also equal to $1/10$. The probability that a galaxy pair populates those surface elements is proportional to the weighted number of galaxies $N_m^i,N_n^j$. We get for $n\neq m$: \[
\mathcal{P}_{mn}^{ij}(\theta) = [1-E(\theta)]\frac{1}{100} N_m^i N_n^j\, .
\label{eq:pmnij_corr1}
\]
For the calculation of $\mathcal{P}_{mm}^{ij}(\theta)$ we have to account for a different possibility: In case that the galaxy lies in the same pointing [accounted for by the factor $E(\theta)$], it automatically is of the same percentile. We therefore set \[
\mathcal{P}_{mm}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j + [1-E(\theta)]\frac{1}{100} N_m^i N_m^j \, .
\label{eq:pmnij_corr2}
\]
We can then write $\mathcal{P}_{mn}^{ij}(\theta)$ as: \[
\mathcal{P}_{mn}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_n^j\,\delta_{mn} + [1-E(\theta)]\frac{1}{100} N_m^i N_n^j \, ,
\label{eq:pmnij_uncorr}
\]
where $\delta_{mn}$ denotes the Kronecker delta.
Inserting this into Eq.\,\eqref{eq:def_xiobs}, we compute
\begin{align}
\xi_{\pm,mn}^{ij,\rm{obs}}(\theta) = & \frac{1}{C}\sum_{m=1}^{10} N_m^i \left\{ E(\theta) N_m^j \xi_{\pm,mm}^{ij}(\theta) + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10}N_n^j \xi_{\pm,mn}^{ij}(\theta)\right\}\, ,
\label{eq:correctionfunction1}
\end{align}
with the normalization
\[
C = \sum_{m=1}^{10} N_m^i \bigg[ E(\theta)  N_m^j + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10} N_n^j\bigg]\, .
\]
A mathematically more rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.

If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate 1275 correlation functions and add them, thus yielding potential numerical errors (apart from being computationally expensive). However, if we examine Eq.\,\eqref{eq:lenseff}, we see that the comoving distance distribution of sources factors in linearly. This in turn implies that in Equations \eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} both source distance distributions factor in linearly. This basically means that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation functions of that. In particular, we can define the \textit{combined number of galaxies} $N^i$ and \textit{average redshift distribution} $p^i(z)$ of tomographic bin $i$ as \[
N^i\equiv\sum_m N_m^i\, , \qquad p^i(z) = \frac{\sum_m N_m^i p_m^i(z)}{\sum_m N_m^i} \, .
\]
If we define $\xi^{ij}_\pm$ as the correlation functions between the average redshift distributions $p^i(z)$ and $p^j(z)$, then we observe: \[
\sum_{m,n}N_m^iN_n^j\xi^{ij}_{\pm,mn} = N^iN^j\xi^{ij}_\pm\, .
\]
Consequently, we can apply this to \eqref{eq:correctionfunction1}, yielding
\begin{equation}
\xi_{\pm}^{ij,\rm{obs}}(\theta) = \frac{1}{C}\left\{ E(\theta)\left[\sum_{m=1}^{10} N_m^iN_m^j \xi_{\pm,mm}^{ij}(\theta)\right] +\frac{\big[1-E(\theta)\big]}{10}\xi_\pm^{ij}(\theta)N^iN^j\right\}\, .
\label{eq:correctionfunction2}
\end{equation}
For each set of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.

@@

\section{Additional Figures}
\subsection{Results of the MCMC}
\begin{figure}[h]
\centering
	\includegraphics[width=0.7\textwidth]{images/obscorr.pdf}
	\caption{Bias in the parameters for a KiDS-like Survey.}
	\label{fig:mcmc_kids}
\end{figure}  
\begin{figure}[h]
\centering
	\includegraphics[width=0.7\textwidth]{images/euclid.pdf}
	\caption{Bias in the parameters for a Euclid-like Survey.}
	\label{fig:mcmc_euclid}
\end{figure}  
\clearpage
\subsection{Finite field effects}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{images/100degtwofoot_final.pdf}
\caption[Correction of the correlation functions for a $100\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $100\,\rm{deg}^2$-field.}
\label{fig:100degsqr}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{images/450degtwofoot_final.pdf}
\caption[Correction of the correlation functions for a $450\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $450\,\rm{deg}^2$-field.}
\label{fig:450degsqr}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{images/1000degtwofoot_final.pdf}
\caption[Correction of the correlation functions for a $1000\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $1000\,\rm{deg}^2$-field.}
\label{fig:1000degsqr}
\end{figure}

>>>>

   \author{S. Heydenreich\inst{1}%\fnmsep\thanks{sven@astro.uni-bonn.de}
          \and Peter Schneider\inst{1} 
          \and Hendrik Hildebrandt\inst{2,1}
          \and Catherine Heymans\inst{3} 
          \and Marika Asgari\inst{3}
          }
   \institute{Argelander-Institut f\"ur Astronomie, Auf dem H\"ugel 71, 53121 Bonn, Germany 
\and 
Astronomisches Institut, Ruhr-Universit\"at Bochum, Universit\"atsstr. 150, 44801 Bochum, Germany \and
Institute for Astronomy, University of Edinburgh, Royal Observatory, Blackford Hill, Edinburgh EH9 3HJ, UK  \\ \email{sven@astro.uni-bonn.de, peter@astro.uni-bonn.de}
             }

@@

To check for remaining systematics, a weak lensing signal can be divided into two components, the so-called E- and B-modes \citep{2002ApJ...568...20C,2002A&A...389..729S}. To leading order, B-modes can not be created by astrophysical phenomena and are thus an excellent test for remaining systematics. The most useful E- and B-mode decomposition is provided by Complete Orthogonal Sets of E- and B-mode Integrals \citep[COSEBIs, compare][]{2010A&A...520A.116S}, as it can easily be applied to real data. Note that the non-existence of B-modes does not necessarily imply that the sample is free of remaining systematics.

@@

The depth of a pointing primarily influences the number density as well as the average redshift of galaxies, meaning that a variation in depth is responsible for a correlation between those two quantities (compare Fig. \ref{fig:nz_of_meanz}).

\begin{figure}
\centering
\includegraphics[width=0.7\linewidth]{images/cov_nz_meanz.pdf}
\caption{Galaxy number density $N$ and average redshift $\la z\ra$ in the KiDS+VIKING-450 (KV450) survey \citep{Wright:2018} in pointings of different depth for each of the five tomographic bins used in H18. Details on how the data was obtained are described in Sec. \ref{sec:xipm_semianalytic}.}
\label{fig:nz_of_meanz}
\end{figure}

@@

\section{Modelling the shear correlation functions}
\label{sec:xipm}
Convenient measures to infer cosmological information from observational data are the shear correlation functions $\xi_\pm$, which are defined as \[
\xi_\pm(\theta) = \la \gamma_{\rm t}\gamma_{\rm t}\ra(\theta) \pm \la \gamma_\times\gamma_\times\ra(\theta) \, .
\]
Here, $\gamma_t$ and $\gamma_\times$ denote the tangential- and cross-component of the shear for a galaxy pair with respect to their relative orientation \citep[compare][]{2002A&A...396....1S}.
The shear correlation functions are the prime estimators to quantify a cosmic-shear signal since it is simple to include a weighting of the shear measurements into the correlation functions and, contrary to the power spectrum, one does not have to worry about the shape of the survey footprint, or masked regions. 
\subsection{Using an analytic model}
\label{sec:xipm_analytic}
For a first simple analysis we will assume that a deeper redshift distribution just yields a stronger shear signal, in the sense that the shear field for a deeper redshift distribution gets multiplied by a weight $W>1$. While this is not true for a 3-dimensional lensing matter distribution, it should be a reasonable first approximation for small variations in mean source redshift. Additionally, we assume that a higher depth does not only lead to a stronger average shear, but also to a higher galaxy number density, implying a correlation between those two quantities.

@@

\subsection{Using a semi-analytic Model}
\label{sec:xipm_semianalytic}
\todo{It feels like some kind of introductory sentence is missing here, right now I can not think of one, though...}
The analysis of data from the Kilo-Degree Survey showed that the redshift distribution of sources is highly correlated with the depth in the $r$-band. We thus chose to separate the survey into 10 percentiles, sorted by $r$-band depth, i.e. if a pointing had a shallower depth than 90\% of the other pointings, it would belong to the first percentile, and so on. For each percentile $m$ and each tomographic redshift bin $i$ we can extract a weighted number of galaxies $N^i_m$ and, a source redshift distribution $p^i_m(z)$ following the DIR method of H17\footnote{Instead of using the actual number of galaxies, we take the sum of their lensing weights, following H17. Due to this we account for different weighting of galaxies on the shear correlation functions as well as on the average redshift distribution.}. Asserting an arbitrary cosmological model, we can transform the source redshift distributions $p^i_m(z)$ into comoving distance probability distributions $\mathcal{L}^i_m(\chi)$.

Given two comoving distance probability distributions of sources $\mathcal{L}^i_m(\chi),\mathcal{L}^j_n(\chi)$, we can compute the shear correlation functions from the underlying matter power spectrum $P(\ell,\chi)$ via \citep[compare][]{1992ApJ...388..272K} \begin{align}
\label{eq:xipm-pkappa}
\xi_{\pm,mn}^{ij}(\theta) =& \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta)\, P^{ij}_{\kappa,mn}(\ell)\, , \\
\label{eq:pkappa-pdelta/lenseff}
P^{ij}_{\kappa,mn}(\ell) =& \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4}\int_0^{\chi_{\rm{H}}} {\rm d}\chi\, \frac{g^i_m(\chi)g^j_n(\chi)}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right)\, , \\
\label{eq:lenseff}
g^i_m(\chi) =& \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, \mathcal{L}^i_m(\chi') \, \frac{f_K(\chi'-\chi)}{f_K(\chi')}\, .
\end{align}
Here, $J_{0,4}$ denote the 0-th and 4-th order Bessel Functions, $f_K(\chi)$ is the comoving angular diameter distance and $\chi_{\rm{H}}$ is chosen such that $p_i(\chi)=0$ holds for all $\chi>\chi_{\rm{H}}$.

Using \eqref{eq:xipm-pkappa}, we can compute the model correlation functions $\xi_{\pm,mn}^{ij}(\theta)$ for each pair of percentiles $m,n$ and redshift bins $i,j$.\footnote{For the calculation of the shear correlation functions we use the \textsc{Nicaea}-program \citep{10.1093/mnras/stx2082}. Among other quantities, it calculates the shear correlation functions for a given cosmology and source redshift distribution. For the power spectrum on nonlinear scales, we use the method of \citet{2012ApJ...761..152T}.} When measuring the shear correlation functions of a survey, we take the weighted average of tangential and cross shears of all pairs of galaxies (compare H17). If, for a single pair of galaxies, one galaxy lies in the $m$-th percentile of redshift bin $i$ and the second one lies in the $n$-th percentile of redshift bin $j$, then their contribution to the observed correlation functions is, on average, $\xi_{\pm,mn}^{ij}(\theta)$. This means that if we know each of those single correlation functions, we can reconstruct the total correlation functions via a weighted average of the single functions. Formally, we define \[
\xi_\pm^{ij,\rm{obs}}(\theta) = \frac{\sum_{m,n} \mathcal{P}_{mn}^{ij}(\theta)\,\xi_{\pm,mn}^{ij}(\theta)}{\sum_{m,n} \mathcal{P}_{mn}^{ij}(\theta)}\, ,
\label{eq:def_xiobs}
\]
where $\mathcal{P}_{mn}^{ij}$ is a weighting of the correlation functions, which has to be proportional to the probability that a galaxy pair of separation $\theta$ comes from percentiles $m$ and $n$.\todo{We \textit{could} completely scratch this derivation and just point to the Appendix; I personally feel that this approach is more intuitive than the more mathematical one of the appendix, but if the paper gets too long we definitely do not need two methods to derive the same equation.} In this analysis, we will assume an infinitely large survey footprint with an uncorrelated distribution of depth. We will later discuss the validity of these assumptions as well as possible mitigation strategies.

To calculate $\mathcal{P}_{mn}^{ij}(\theta)$ we imagine two arbitrary (infinitesimally small) surface elements $\d^2\b\theta_1,\d^2\b\theta_2$ of separation $\theta$ on the sky. For the case $m\neq n$ we know that a pair of galaxies contributing to $\mathcal{P}_{mn}^{ij}(\theta)$ has to lie in different pointings, else they would automatically be of the same percentile. The probability that the imagined surface elements are within different pointings is $[1-E(\theta)]$. Furthermore, the first element $\d^2\b\theta_1$ has to lie in percentile $m$, the probability of which is $1/10$. The pointing of the second element $\d^2\b\theta_2$ has to be of percentile $n$; the probability of that is also equal to $1/10$. The probability that a galaxy pair populates those surface elements is proportional to the weighted number of galaxies $N_m^i,N_n^j$. We get for $n\neq m$: \[
\mathcal{P}_{mn}^{ij}(\theta) = [1-E(\theta)]\frac{1}{100} N_m^i N_n^j\, .
\label{eq:pmnij_corr1}
\]
For the calculation of $\mathcal{P}_{mm}^{ij}(\theta)$ we have to account for a different possibility: In case that the galaxy lies in the same pointing [accounted for by the factor $E(\theta)$], it automatically is of the same percentile. We therefore set \[
\mathcal{P}_{mm}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j + [1-E(\theta)]\frac{1}{100} N_m^i N_m^j \, .
\label{eq:pmnij_corr2}
\]
We can then write $\mathcal{P}_{mn}^{ij}(\theta)$ as: \[
\mathcal{P}_{mn}^{ij}(\theta) = E(\theta)\frac{1}{10} N_m^iN_m^j\,\delta_{mn} + [1-E(\theta)]\frac{1}{100} N_m^i N_n^j \, ,
\label{eq:pmnij_uncorr}
\]
where $\delta_{mn}$ denotes the Kronecker delta.
Inserting this into Eq.\,\eqref{eq:def_xiobs}, we compute
\begin{align}
\xi_{\pm,mn}^{ij,\rm{obs}}(\theta) = & \frac{1}{C}\sum_{m=1}^{10} N_m^i \left\{ E(\theta) N_m^j \xi_{\pm,mm}^{ij}(\theta) + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10}N_n^j \xi_{\pm,mn}^{ij}(\theta)\right\}\, ,
\label{eq:correctionfunction1}
\end{align}
with the normalization
\[
C = \sum_{m=1}^{10} N_m^i \bigg[ E(\theta)  N_m^j + \frac{\big[1-E(\theta)\big]}{10}\sum_{n=1}^{10} N_n^j\bigg]\, .
\]
A mathematically more rigorous derivation of this function can be found in Appendix \ref{sec:calc of xipm}.

If we want to compute this for all 5 redshift bins of the KV450-survey, this forces us to calculate 1275 correlation functions and coadding them, thus yielding potential numerical errors (apart from being computationally expensive). However, if we examine Eq.\,\eqref{eq:lenseff}, we see that the comoving distance distribution of sources enters linearly. This in turn implies that in Equations \eqref{eq:pkappa-pdelta/lenseff} and \eqref{eq:xipm-pkappa} both source distance distributions enter linearly, meaning that, instead of adding correlation functions, we can add their respective redshift distributions and compute the correlation functions of that. In particular, we can define the \textit{combined number of galaxies} $N^i$ and \textit{average comoving distance probability distribution} $\mathcal{L}^i(\chi)$ of tomographic bin $i$ as \[
N^i\equiv\sum_m N_m^i\, , \qquad \mathcal{L}^i(\chi) = \frac{\sum_m N_m^i \mathcal{L}_m^i(\chi)}{\sum_m N_m^i} \, .
\]
If we define $\xi^{ij}_\pm$ as the correlation functions between the average comoving distance distributions $\mathcal{L}^i(\chi)$ and $\mathcal{L}^j(\chi)$, then we observe: \begin{align}
\sum_{m,n}N_m^iN_n^j\xi^{ij}_{\pm,mn} = & \, \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4} \sum_{m,n} N_m^i N_n^j \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta) \int_0^{\chi_{\rm{H}}} \frac{{\rm d}\chi}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right) \\
& \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, \mathcal{L}^i_m(\chi') \, \frac{f_K(\chi'-\chi)}{f_K(\chi')}
\int_\chi^{\chi_{\rm{H}}} {\rm d}\chi'' \, \mathcal{L}^j_n(\chi'') \, \frac{f_K(\chi''-\chi)}{f_K(\chi'')} \\
 = & \,N^i N^j \, \frac{9 H_0^4\Omega_{\rm m}^2}{4c^4} \int_0^\infty \frac{{\rm d}\ell\,\ell}{2\pi}\, J_{0,4}(\ell\theta) \int_0^{\chi_{\rm{H}}} \frac{{\rm d}\chi}{a^2(\chi)}\, P_\delta\left(\frac{\ell}{f_K(\chi)},\chi\right) \\
& \int_\chi^{\chi_{\rm{H}}} {\rm d}\chi' \, \frac{\sum_m N_m^i \mathcal{L}^i_m(\chi')}{N^i} \, \frac{f_K(\chi'-\chi)}{f_K(\chi')}
\int_\chi^{\chi_{\rm{H}}} {\rm d}\chi'' \, \frac{\sum_n N_n^j \mathcal{L}^j_n(\chi'')}{N^j}  \, \frac{f_K(\chi''-\chi)}{f_K(\chi'')} \\
 = & \, N^iN^j\xi^{ij}_\pm\, ,
\end{align}
where $\xi^{ij}_\pm$ denotes the correlation function for the average comoving distance probability distributions of redshift bins $i$ and $j$.
Consequently, we can apply this to \eqref{eq:correctionfunction1}, yielding
\begin{equation}
\xi_{\pm}^{ij,\rm{obs}}(\theta) = \frac{1}{C}\left\{ E(\theta)\left[\sum_{m=1}^{10} N_m^iN_m^j \xi_{\pm,mm}^{ij}(\theta)\right] +\frac{\big[1-E(\theta)\big]}{10}\xi_\pm^{ij}(\theta)N^iN^j\right\}\, .
\label{eq:correctionfunction2}
\end{equation}
For each pair of redshift bins we thus only have to compute eleven correlation functions, which reduces the number of functions to compute from 1275 to 165.

@@

\section{Additional Figures}
\subsection{Results of the MCMC}
\begin{figure}[h]
\centering
	\includegraphics[width=0.7\textwidth]{images/mcmc_kids.pdf}
	\caption{Bias in the parameters for a KiDS-like Survey.}
	\label{fig:mcmc_kids}
\end{figure}  
\begin{figure}[h]
\centering
	\includegraphics[width=0.7\textwidth]{images/mcmc_euclid.pdf}
	\caption{Bias in the parameters for a Euclid-like Survey.}
	\label{fig:mcmc_euclid}
\end{figure}  
\clearpage
\subsection{Finite field effects}

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{images/finite_footprint.pdf}
\caption[Correction of the correlation functions for a $100\,\rm{deg}^2$-field.] {Correction of the correlation functions for two different distributions of percentiles for a $100\,\rm{deg}^2$-field.}
\label{fig:100degsqr}
\end{figure}
